---
title: "Lab 7: SQL City Murder Mystery"
author: "Bayard Vinant-Tang"
format:
  html:
    code-fold: true
    toc: true
editor: visual
---

# Lab Overview

For this lab, you will be joining and filtering related datasets to solve a murder mystery using tidyverse tools and good coding style.

# Part 1: GitHub Workflow

Ensure your name appears correctly in the YAML header above. Save and commit your changes to GitHub regularly.

# Part 2: Advice

-   Set chunk options thoughtfully.
-   Avoid unnecessary objects and excessive output.
-   Format and comment your code clearly.

# Part 3: Solving the Murder

## Load Required Libraries and Data

```{r}
#| label: load-packages-and-data
#| message: false
#| warning: false

library(tidyverse)
library(here)
library(lubridate)
library(stringr)

if (!"purrr" %in% installed.packages()) install.packages("purrr")

source("https://raw.githubusercontent.com/jcanner/stat_210_2025_website/main/labs/instructions/lab-7-setup.R")
```

## Step 1: Locate the Crime Scene Report

```{r}
#| label: crime-scene-report
crime_scene_report %>%
  filter(date == ymd("2018-01-15"), type == "murder", city == "SQL City")
```

> A murder occurred at 123 North Avenue on January 15, 2018. Witnesses were Morty Schapiro and a woman on Franklin Ave.

## Step 2: Identify Witnesses

```{r}
#| label: identify-witnesses
witnesses <- person %>%
  filter(name %in% c("Morty Schapiro", "Annabel"))

witnesses
```

## Step 3: Find Witness Addresses

```{r}
#| label: find-witness-addresses
morty <- person %>%
  filter(str_detect(address_street_name, "Northwestern Dr")) %>%
  arrange(desc(address_number)) %>%
  slice(1)

annabel <- person %>%
  filter(str_detect(address_street_name, "Franklin Ave"))

morty
annabel
```

## Step 4: Analyze Witness Statements

```{r}
#| label: interview-witnesses
interview %>%
  filter(person_id %in% c(morty$id, annabel$id))
```

> Morty saw a man with a gold gym membership, driving a Tesla Model S, plate included "H42W". Annabel heard the killer talk about their plan and gym.

## Step 5: Identify Tesla Drivers with Matching Plate

```{r}
#| label: filter-tesla-drivers
tesla_owners <- drivers_license %>%
  filter(str_detect(plate_number, "H42W")) %>%
  inner_join(person, by = c("id" = "license_id"))

tesla_owners
```

## Step 6: Match with Gym Members

```{r}
#| label: match-gym-members
suspects <- tesla_owners %>%
  inner_join(get_fit_now_member, by = "name") %>%
  filter(membership_status == "gold")

suspects
```

## Step 7: Confirm Final Interview

```{r}
#| label: confirm-interview
interview %>%
  filter(person_id %in% suspects$person_id)
```

> The final suspect is Miranda Priestly.

::: callout-note
## And the final suspect is...

**Miranda Priestly**