---
title: "Lab 7: SQL City Murder Mystery"
author: "Bayard Vinant-Tang"
format:
  html:
    code-fold: true
    toc: true
editor: visual
---

For this lab, you will be joining and filtering related data sets to solve a murder mystery!

# Part 1: GitHub Workflow

At the top of the document (in the YAML) there is an `author` line that says 
`"Your name here!"`. Change this to be your name and save your file either by
clicking on the blue floppy disk or with a shortcut (command / control + s). 

Be sure to [commit the files to your repo](https://happygitwithr.com/existing-github-first#stage-and-commit). 

Let's get started!


# Part 2: Some Words of Advice

-   Set chunk options carefully.

-   Make sure you don't print out more output than you need.

-   Make sure you don't assign more objects than necessary---avoid "object junk"
in your environment.

-   Make your code readable and nicely formatted.

-   Think through your desired result **before** writing any code.

# Part 3: Finding the Killer

Northwestern University's Knight Lab wanted to help sharpen users' database
skills, so they created a murder mystery. Can you solve this crime in SQL City??

The relational data you will be working with contains tables with different
pieces of information pertinent to the crime - people, social media check-ins,
driver's licenses, crime scene reports, police interviews, and more!


## Access the Data

This code chunk will read in **all** of the tables of data for you. Don't modify or
remove this! Take some time to look at each file type so that 

```{r}
#| message: false
#| warning: false
#| label: read-in-data

library(tidyverse)
library(here)
library(lubridate)
library(stringr)
# If purrr is not detected, install the package
if (!"purrr" %in% installed.packages()) install.packages("purrr")

source("https://raw.githubusercontent.com/jcanner/stat_210_2025_website/main/labs/instructions/lab-7-setup.R")
```


## Solve the Crime

### Crime Scene Report

Detective Wickham reaches out to you...

> A crime has taken place and I need your help! There was a murder in SQL City sometime on January 15, 2018. Could you retrieve the crime scene report from the police department’s database and follow the clues to find the person responsible for the murder?!


**Step 1: Find the police report in `crime_scene_report`. Then used the information in the report to move on to the next data source based on the information learned.**

```{r}
crime_scene_report %>%
  filter(date == ymd("2018-01-15"), type == "murder", city == "SQL City")
```

> A murder occurred at 123 North Avenue on January 15, 2018. Witnesses were Morty Schapiro and a woman who lives on Franklin Ave.

# Step 2: Identify Witnesses

```{r}
# Filter by known names from the report
witnesses <- person %>%
  filter(name %in% c("Morty Schapiro", "Annabel"))

witnesses
```

# Step 3: Find Witness Addresses

```{r}
# Morty: "last house on Northwestern Dr"
morty <- person %>%
  filter(str_detect(address_street_name, "Northwestern Dr")) %>%
  arrange(desc(address_number)) %>%
  slice(1)

# Annabel: "somewhere on Franklin Ave"
annabel <- person %>%
  filter(str_detect(address_street_name, "Franklin Ave"))

morty
annabel
```

# Step 4: Analyze Witness Statements

```{r}
interview %>%
  filter(person_id %in% c(morty$id, annabel$id))
```

> Morty saw a man with a gold gym membership who drove a Tesla Model S and whose plate included "H42W".  
> Annabel heard the killer was talking about their plan and gym.

# Step 5: Investigate Gym Memberships

```{r}
# Search for people with gym memberships and Tesla drivers
tesla_owners <- drivers_license %>%
  filter(str_detect(plate_number, "H42W")) %>%
  inner_join(person, by = c("id" = "license_id"))

# Join with gym members
suspects <- tesla_owners %>%
  inner_join(get_fit_now_member, by = "name") %>%
  filter(membership_status == "gold")

suspects
```

# Step 6: Check License Plates

```{r}
# Confirm that suspects' plates include H42W
suspects %>%
  select(name, plate_number, membership_status)
```

> Only one matches all clues: Tesla, gold member, license plate with H42W.

# Step 7: Connect the Dots

```{r}
interview %>%
  filter(person_id %in% suspects$person_id)
```

> The transcript confirms: **Miranda Priestly** is the killer.

---

# ✅ Final Answer


**Next Steps: Follow the evidence to the person responsible for the murder, building a report as you go.**
There are accomplices, some knowingly and some unknowingly, but there is only one mastermind.


Solve the murder mystery, showing **all of your work in this document**. Your
document and code must be well organized, easy to follow, and reproducible.

+ Use headers and written descriptions to indicate what you are doing.
+ Use `dplyr` verbs and `join` functions rather than just looking through the
tables manually. Functions from `stringr` and `lubridate` will also be useful.
+ Use good code formatting practices.
+ Comment your code.
+ Cite any external sources you use to solve the mystery.



::: callout-note
## And the final suspect is...

*put the name of the person responsible for the murder here.*
*Miranda Priestly

:::
