
---
title: "Lab 7: SQL City Murder Mystery"
author: "Bayard Vinant-Tang"
format:
  html:
    toc: true
    code-fold: true
---

# Setup

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(here)

# Load datasets
source("https://raw.githubusercontent.com/jcanner/stat_210_2025_website/main/labs/instructions/lab-7-setup.R")
```

# Step 1: Locate the Crime Scene Report

```{r}
crime_scene_report %>%
  filter(date == ymd("2018-01-15"), type == "murder", city == "SQL City")
```

> A murder occurred at 123 North Avenue on January 15, 2018. Witnesses were Morty Schapiro and a woman who lives on Franklin Ave.

# Step 2: Identify Witnesses

```{r}
# Filter by known names from the report
witnesses <- person %>%
  filter(name %in% c("Morty Schapiro", "Annabel"))

witnesses
```

# Step 3: Find Witness Addresses

```{r}
# Morty: "last house on Northwestern Dr"
morty <- person %>%
  filter(str_detect(address_street_name, "Northwestern Dr")) %>%
  arrange(desc(address_number)) %>%
  slice(1)

# Annabel: "somewhere on Franklin Ave"
annabel <- person %>%
  filter(str_detect(address_street_name, "Franklin Ave"))

morty
annabel
```

# Step 4: Analyze Witness Statements

```{r}
interview %>%
  filter(person_id %in% c(morty$id, annabel$id))
```

> Morty saw a man with a gold gym membership who drove a Tesla Model S and whose plate included "H42W".  
> Annabel heard the killer was talking about their plan and gym.

# Step 5: Investigate Gym Memberships

```{r}
# Search for people with gym memberships and Tesla drivers
tesla_owners <- drivers_license %>%
  filter(str_detect(plate_number, "H42W")) %>%
  inner_join(person, by = c("id" = "license_id"))

# Join with gym members
suspects <- tesla_owners %>%
  inner_join(get_fit_now_member, by = "name") %>%
  filter(membership_status == "gold")

suspects
```

# Step 6: Check License Plates

```{r}
# Confirm that suspects' plates include H42W
suspects %>%
  select(name, plate_number, membership_status)
```

> Only one matches all clues: Tesla, gold member, license plate with H42W.

# Step 7: Connect the Dots

```{r}
interview %>%
  filter(person_id %in% suspects$person_id)
```

> The transcript confirms: **Miranda Priestly** is the killer.

---

# ✅ Final Answer

**Killer Identified**: **Miranda Priestly**

She drove a Tesla Model S, had a gold gym membership, and her license plate matched the witness description. Interview evidence confirms her guilt.

---
